Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-07-05 dis_clusion.tex
new proposition for Model B scaling description

\section{Conclusion and futur work}

This work has investigated and quantified the difference between potential
models for retuning of a centrifuge enrichment cascade in order to chain them to produce
\gls{HEU} initially tuned to produce uranium enrichment for commercial reactors.
One of these tuning method achieves up to $80\%$ of the production rate of a single
large enrichment cascade designed specifically for \gls{HEU} production using
the same number of centrifuges.

>>>>

\section{Conclusion and future work}

This work has investigated the possibility to chain centrifuge enrichment
cascades designed to enrich uranium for commercial reactors in order to
produce \gls{HEU}. Three methods have been implemented to model enrichment
cascade behavior when fed with different uranium enrichment than the designed
enrichment.

%% This work has investigated and quantified the difference between potential
%% models for retuning of a centrifuge enrichment cascade in order to chain them to produce
%% \gls{HEU} initially tuned to produce uranium enrichment for commercial reactors.
One of these method achieves up to $80\%$ of the production rate of a single
large enrichment cascade designed specifically for \gls{HEU} production using
the same number of centrifuges.

### 2018-07-05 theory.tex
new proposition for Model B scaling description

As the cut values change, the relative flow rates between the different stage
are recomputed using equation \eqref{eq:flow}. The flow rates are determinted as
the largest flow rates allowed by the cascade design, number of centrifuges
limiting the flow at each stage.

>>>>

As the cut values change, the relative flow rates between the different stage
are recomputed using equation \eqref{eq:flow}. 
The new relative flow rates are compared stage by stage to the flow rates allowed by the
cascade design, the number of centrifuges per stage limiting the flow. The new
absolute flow rates are computed by scaling the relative flow rates using the most
limiting stage.

%% The flow rates are determinted as
%% the largest flow rates allowed by the cascade design, number of centrifuges
%% limiting the flow at each stage.
